---
title: "POS503 Assignment 1"
author: "Hao Wang"
date: "Sep. 4, 2016"
output: pdf_document
header-includes: \usepackage{float}
---

Analysis is done in R, required packages for replcating results are listed. Document is created by R Markdown.

```{r setup, echo=TRUE, warning=FALSE, message=FALSE}
#setwd("D:/Dropbox/2016 Fall/POS 503 Inquiry/Assignment/Assignment 1")
#setwd("~/Dropbox/2016 Fall/POS 503 Inquiry/Assignment/Assignment 1")options(digits=10)
library(ggplot2)
library(knitr)
library(rmarkdown)
library(foreign)
```

#Accessing Data
The following R chunk load data from Baylor Regilious Survey. Baylor Religious Study is a comprehensive analysis on religious beliefs in the United States. For detailed explanation please refer to <http://www.thearda.com/Archive/Files/Descriptions/BAYLORW2.asp>. Total sample size is 1648 adults, with 318 variables, survey was conducted by Gallup. 


```{r}
#The first step is to load Byalor Religious Survey 2005 (I)
mydata <- read.dta("http://www.thearda.com/download/download.aspx?file=Baylor%20Religion%20Survey,%20Wave%20II%20(2007).DTA")
```

#Scatter Plot
Because the raw file includes some missing points, I create a new dataset of potential interesting variables without missing data.

```{r, warning=FALSE, message=FALSE}
plotdata <- mydata[, c('relgious', 'attend', 'gaymarr', 'gayborn',
                       'votefem', 'partyid')]
#religious: how religious you are
#attend:    how often do you attend church
#gaymarr:   gay marriage should be legal
#gayborn:   people are born either homo or heterosexual
#vetefem:   would you vote for a female cadidate nominated by your party
#partyid:   democract or republican
plotdata <- na.omit(plotdata)
summary(plotdata)
plotdata2=as.data.frame(sapply(plotdata, as.numeric))#sapply function returns matrix with same
#legnth, and in the same time converted factors into numeric numbers by as.numeric command
```

##The first plot is religious belief and gay marriage.

```{r, warning=FALSE}
table(plotdata$gaymarr, plotdata$relgious)
relig.gaymarr <- ggplot(data=plotdata, aes(x = relgious, y = gaymarr)) +
                 geom_count() +
                 scale_size_area()
relig.gaymarr

```
From the table and plot, we can observe an negative relation between religious belief and support for gay marriage. 

##The second plot is religious belief and vote for female candidate.

```{r, warning=FALSE}
table(plotdata$votefem, plotdata$relgious)
relig.votefem <- ggplot(data=plotdata, aes(x = relgious, y = votefem)) +
                 geom_count() +
                 scale_size_area()
relig.votefem

```

Result here is not very obvious, for a detailed analysis I perform the following steps.

```{r}
table(plotdata2$votefem, plotdata2$relgious)
table(plotdata$votefem, plotdata$relgious)
plotdata2$fem <- (plotdata2$votefem -2)^2
#This step is to change the levels of fem variable.
plotdata3     <- data.frame(subset(plotdata2, plotdata2[ , 'relgious'] < 5))
#This step is to get rid of the unknown option
```

Then use probit funtion to predict probability

```{r}

Myprobit <- glm(fem ~ relgious, 
                family=binomial(link="probit"), data=plotdata3)
relgious  <-  seq(from = 1, to =  4, by = 0.01)
newdata1 <-  data.frame(relgious)
summary(Myprobit)

```

This step is to display the marginal effect.
```{r}

p1 = predict.glm(Myprobit,newdata = newdata1, type="response", se.fit=TRUE)
mar1 = p1$fit
up   = mar1 + 1.96*p1$se.fit
low  = mar1 - 1.96*p1$se.fit

Marplot <- ggplot(data=newdata1, aes(x = relgious))+ geom_line(aes(y =mar1)) + 
  geom_line(aes(y =up), linetype="dashed") + 
  geom_line(aes(y =low), linetype="dashed") + 
  xlab("Religious Beliefs (ranging from not at all religious to very religious)") +
  ylab("Predicted Probability") +
  ggtitle("Marginal Effect of Religious Beliefs on Female Candidate Vote Intention")
  #+geom_histogram(sides="b")+
  #geom_rug()

Marplot
```

As we can see from the Myprobit result as well as the marginal effect plot, religious beliefs has a significant effect on decreasing the intention of voting for a female candidate. 


